Title

### 2019-05-05 paper_notes.Rmd
Update paper_notes.Rmd

- Object of choice: neighborhood
- Choice: relocate to a neighborhood
- Utility: payoff one is likely to accept to make the choice, i.e. to relocate to one neighborhood (which implies to stay on the same neighborhood). In @zhang2004 it is made up of:
  - deterministic component $U$: how much people desire/value one preference  in order to make the choice, e.g. degree of ethnic concentration (e.g. max utility = 1 at 100% similars). @zhang2004 uses a single-peaked function (vs maximization).
  - random term $\epsilon$ that refers to other characteristics of the option, i.e. the neighborhood, that influence the payoff to choose the neighborhood although not related to the deterministic component. In regression models  this is the random  error terms. Random utility models in abm recreate with the exponential function, so that not always the best option according to the deterministic component is taken.
- Probability of the choice: $\beta u (.) + \epsilon$\
$\beta$ is a parameter indicating how much the random term is important modeled as a positive constant. The lower is \$beta\, the higher is random term $\epsilon$, i.e. other random characteristics, are relevant to choose one neighborhood. The higher is $\beta$, the lower will be the importance of random term $\epsilon$ and higher the importance of deterministic utility component to make a choice, i.e. moving to the neighborhood.
\
- Given the existence of an ideal payoff to make a choice $u$, why should someone give more importance to that dimension over the other, that is, why should $\beta$ vary among individuals? An answer in @esser2010 is social, educational, economic capital. For instance:
  - The lower an agent speaks a language, the higher for ethnic homophily would be  $\beta_{ethnic}$;
  - the higher is social mobility intention, the higher the wealth (socio-economic status) of the neighborhood would be $\beta_{status}$
  - the higher the need to associate with people sharing the same values of local community (receiving context in Esser [@esser2010] (e.g. political orientations, norm beliefs...), the higher 
- Seemingly, @zhang2004 describes $\epsilon$ as other characteristics of the option which affects the actual choice of that option (i.e. neighborhood). Esser's [@esser2010] definition of costs of the choice can be taken into consideration, as costs of moving to the neighborhood.

@@

- The formula $\beta u (.) + \epsilon$ should become somthing like $$N_{e} U_{e} + N_{v} U_{v} + N_{s} U_{s} - C$$ where $N$ =  needs, $C$ = costs and $e,v,s$ the ethnic, value and socio-economic status dimension.

>>>>

- Object of choice: neighborhood
- Choice: relocate to a neighborhood
- Utility: payoff one is likely to accept to make the choice, i.e. to relocate to one neighborhood (which implies to stay on the same neighborhood). In @zhang2004 it is made up of:
  - deterministic component $U$: how much people desire/value one preference  in order to make the choice, e.g. degree of ethnic concentration (e.g. max utility = 1 at 100% similars). @zhang2004 uses a single-peaked function (vs maximization).
  - random term $\epsilon$ that refers to other characteristics of the option, i.e. the neighborhood, that influence the payoff to choose the neighborhood although not related to the deterministic component. In regression models  this is the random  error terms. Random utility models in abm recreate with the exponential function, so that not always the best option according to the deterministic component is taken.
- Probability of the choice: $\beta u (.) + \epsilon$\
$\beta$ is a parameter indicating how much the random term is important modeled as a positive constant. The lower is \$beta\, the higher is random term $\epsilon$, i.e. other random characteristics, are relevant to choose one neighborhood. The higher is $\beta$, the lower will be the importance of random term $\epsilon$ and higher the importance of deterministic utility component to make a choice, i.e. moving to the neighborhood.
\
- Given the existence of an ideal payoff to make a choice $u$, why should someone give more importance to that dimension over the other, that is, why should $\beta$ vary among individuals? An answer in @esser2010 is social, educational, economic capital. For instance:
  - The lower an agent speaks a language, the higher for ethnic homophily would be  $\beta_{ethnic}$;
  - the higher is social mobility intention, the higher the wealth (socio-economic status) of the neighborhood would be $\beta_{status}$
  - the higher the need to associate with people sharing the same values of local community (receiving context in Esser [@esser2010] (e.g. political orientations, norm beliefs...), the higher 
- Costs of relocation can be included as costs that hinder relocation despite high probability to choose. This can be one application of  @esser2010's definition of costs as limit to the investment on the receving context option (although in the ethnic population, but it can be extended). In @esser2010 costs is loosely derived from social, economic and cultural capital milieu, e.g. risk of social exclusion from in-group, but economic costs of relocation can be one simple implementation now.

@@

- The formula $\beta u (.) + \epsilon$ should become something like $$N_{e} U_{e} + N_{v} U_{v} + N_{s} U_{s} - C$$ where $N$ =  needs, $C$ = costs and $e,v,s$ the ethnic, value and socio-economic status dimension. The random term $\epsilon$ is implemented through the exponential function.
